Exploring variables in the data

### 2017-08-03 variable_exploration.Rmd
started fitting CR model, reorganized/added to files, updated hours

library(ggplot2)
library(survival)
library(epiR)
library(stringr)
library(rebus)
```

```{r, functions, include = FALSE}
#function to plot KM_curves with ggplot (use when it's hard to read ggsurvplot output)
#takes survfit object, data set to work with, and optional x-axis limits as input, outputs ggplot KM curves

plot_surv <- function(survfit, data, xlim = NULL) {
  library(ggfortify)
  library(directlabels)

@@

```

@@

##### number of questions within each category

```{r, echo = FALSE}
x %>%
  group_by(category) %>%
  summarise(n = n()) %>%
  arrange(desc(n))
```

##### median/average time by category

```{r, echo = FALSE}
sorted <- x %>% 
  group_by(category) %>%
  summarise(n = n(), avg_time = mean(time_until_answer), median_time = median(time_until_answer), median_views = median(daily_views)) %>%
  arrange(median_time)
sorted
```

* **Categories with lowest median time_until_answer values:** `r as.character(sorted$category[1:5])`
* **Category with longest median time_until_answer:** `r last(as.character(sorted$category))`

@@

##### Is there a difference between iphone and android users?

```{r, echo = FALSE}
x %>% 
  filter(subcategory == c("iPhone", "Android Phone")) %>%
  group_by(subcategory) %>%
  summarise(median_time = median(time_until_answer), n = n(), avg_views = mean(daily_views))
```

@@

survdiff(surv_object~categorized, data = x)
```

##### survival curves

```{r, echo = FALSE}
KM_correct <- survfit(surv_object ~ as.factor(categorized), data = x)
plot_surv(KM_correct, data = x, xlim = c(0,100))
```

@@

ggplot(x, aes(x = title_length)) + 
  geom_histogram() + 
  scale_x_continuous("Length of Question Title") + 
  ggtitle("Distribution of Title Lengths")

sum_length <- summary(x$title_length)
```

* **min title length:** `r sum_length[1]` characters
* **max title length:** `r sum_length[6]` characters
* **mean title length:** `r sum_length[4]`
* **median:** `r sum_length[3]`

@@

```{r, echo = FALSE}
x %>%
  group_by(as.factor(answered)) %>%
  summarise(avg_titlelength = mean(title_length), median_titlelength = median(title_length), n = n())
```

@@

ggplot(x, aes(x = text_length)) + 
  geom_histogram() + 
  scale_x_continuous("Length of Text") + 
  ggtitle("Distribution of Text Lengths")

sum_text <- summary(x$text_length)
```

* **min text length:** `r sum_text[1]` characters
* **max text length:** `r sum_text[6]` characters
* **mean text length:** `r sum_text[4]`
* **median:** `r sum_text[3]`

@@

```{r, echo = FALSE}
x %>%
  group_by(as.factor(answered)) %>%
  summarise(avg_length = mean(text_length), median_length = median(text_length), median_time = median(time_until_answer), n = n())
```

@@

```{r, echo = FALSE}
x %>%
  group_by(category) %>%
  summarise(avg_length = mean(text_length), median_length = median(text_length), n = n()) %>%
  arrange(desc(avg_length))
```

@@

ggplot(x, aes(x = device_length)) + 
  geom_histogram() + 
  scale_x_continuous("Length of Device Name") + 
  ggtitle("Distribution of Device Name Lengths")

sum_device <- summary(x$device_length)
```

* **min length:** `r sum_device[1]`
* **max length:** `r sum_device[6]`
* **mean length:** `r sum_device[4]`
* **median length:** `r sum_device[3]`

@@

```{r, echo = FALSE}
x %>%
  group_by(as.factor(answered)) %>%
  summarise(avg_length = mean(device_length), median_length = median(device_length), n = n())
```

@@

```{r, echo = FALSE}
x %>%
  group_by(category) %>%
  summarise(avg_length = mean(device_length), median_length = median(device_length), n = n(), median_time = median(time_until_answer)) %>%
  arrange(desc(avg_length))
```

@@

* n_tags included in questions: `r unique(x$n_tags)`
```{r, echo = FALSE}
prop_notags <- sum(x$n_tags == 0)/nrow(x)
```
* `r round(prop_notags * 100,2)`% of questions don't have any tags

@@

```{r, echo = FALSE}
x %>%
  group_by(as.factor(n_tags)) %>%
  summarise(n = n(), median_time = median(time_until_answer), proportion_answered = sum(answered)/n, median_views = median(daily_views)) %>%
  arrange(median_time)
```

@@

x %>%
  group_by(as.factor(pic_included)) %>%
  summarise(median_time = median(time_until_answer), n = n(), proportion_answered = sum(answered)/n, median_views = median(daily_views)) %>%
  arrange(desc(proportion_answered))
```

@@

```{r, echo = FALSE}
survdiff(surv_object ~ as.factor(pic_included), data = x)
KM_pic <- survfit(surv_object~as.factor(pic_included), data = x)
plot_surv(KM_pic, data = x)
```

@@

```{r, echo = FALSE}
x %>% 
  group_by(as.factor(new_user)) %>%
  summarise(median_time = median(time_until_answer), n = n(), proportion_answered = sum(answered)/n) %>%
  arrange(desc(proportion_answered))
```

@@

```{r}
x$post_datetime <- as.POSIXct(x$post_date,origin="1970-01-01")
x$post_d <- format(x$post_datetime, "%m/%d/%y")
x$post_time <- format(x$post_datetime, " %H:%M:%S")
x$post_weekday <- factor(weekdays(x$post_datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
x$post_hour <- as.numeric(format(x$post_datetime,"%H"))

@@

```{r, echo = FALSE}
x %>%
  group_by(post_weekday) %>%
  summarise(median_time = median(time_until_answer), avg_views = mean(daily_views), n = n(), prop_answered = sum(answered)/n) %>%
  arrange(median_time)
```

@@

```{r, echo = FALSE}
x %>%
  group_by(as.factor(post_hour)) %>%
  summarise(n = n(), median_time = median(time_until_answer), avg_views = mean(daily_views), prop_answered = sum(answered)/n) %>%
  arrange(median_time)

```

##### Median time grouped by morning/afternoon

```{r, echo = FALSE}
x %>%
  group_by(post_ampm) %>%
  summarise(median_time = median(time_until_answer), avg_views = mean(daily_views), n = n(), prop_answered = sum(answered)/n)
```

@@

>>>>

library(ggplot2)
library(survival)
library(epiR)
library(stringr)
library(rebus)
library(qdap)
library(tm)
```

```{r, functions, include = FALSE}
#function to plot KM_curves with ggplot (use when it's hard to read ggsurvplot output)
#takes survfit object, data set to work with, and optional x-axis limits as input, outputs ggplot KM curves
plot_surv <- function(survfit, data, xlim = NULL) {
  library(ggfortify)
  library(directlabels)

@@

#function that prints out summary stats grouped by that variable 
sum_stats <- function(variable, data) {
  tbl <- x %>%
    group_by(data[[variable]]) %>%
    summarise(n = n(), median_time = median(time_until_answer), median_views = median(daily_views), prop_answered = sum(answered)/n) %>%
    arrange(median_time)
  names(tbl)[1] <- variable
  return(tbl)
}

#took out phone iphone and android

#function to clean corpus (stopwrds is an optional argument)
clean_corpus <- function(corpus, stopwrds = NULL){
  if (is.null(stopwrds)) {
    corpus <- tm_map(corpus, stripWhitespace)
    corpus <- tm_map(corpus, content_transformer(tolower))
    corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "can", "will", "cant", "wont", "works", "get", "help", "need", "fix"))
    return(corpus)    
  } else {
    corpus <- tm_map(corpus, stripWhitespace)
    corpus <- tm_map(corpus, content_transformer(tolower))
    corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "can", "will", "cant", "wont", "works", "get", "help", "need", "fix", stopwrds))
    return(corpus)
  }
}

#function that takes in character vector and returns a data frame of words and frequencies sorted by most to least frequent, n and stopwrds are an optional arguments
freq_terms <- function(vec, n = NULL, stopwrds = NULL) {
  source <- VectorSource(vec)
  corpus <- VCorpus(source)

  if (is.null(stopwrds)) {
    cleaned_corpus <- clean_corpus(corpus) 
    dtm <- DocumentTermMatrix(cleaned_corpus, control = list(weighting = weightTfIdf))
    m <- as.matrix(dtm) 
    freq <- colSums(m)
    freq <- sort(freq, decreasing = TRUE)
    freq_df <- data.frame(word = names(freq), frequency = unname(freq))    
  } else {
    cleaned_corpus <- clean_corpus(corpus, stopwrds) 
    dtm <- DocumentTermMatrix(cleaned_corpus, control = list(weighting = weightTfIdf))
    m <- as.matrix(dtm) 
    freq <- colSums(m)
    freq <- sort(freq, decreasing = TRUE)
    freq_df <- data.frame(word = names(freq), frequency = unname(freq))
  }

  if (missing(n)) {
    return(freq_df)
  }
  else {
    return(freq_df[1:n,])
  }
}
```

@@

##### summary stats grouped by category, arranged by median time

* NA's represent questions for devices that don't already exist on the website, treat as other?

```{r, echo = FALSE}
sum_stats("category", x)
```

@@

### Subcategories

```{r, echo = FALSE}
x %>%
  group_by(subcategory) %>%
  summarise(n = n(), proportion = n/nrow(x), prop_ans = sum(answered)/n, median_time = median(time_until_answer)) %>%
  arrange(desc(n))
```

##### Is there a difference between iPhone and Android users?

```{r, echo = FALSE}
x %>% 
  filter(subcategory == c("iPhone", "Android Phone")) %>%
  group_by(subcategory) %>%
  summarise(n = n(), median_time = median(time_until_answer), median_views = median(daily_views), prop_ans = sum(answered)/n)
```

##### textmining on iPhone and Android Phone text

##### Word cloud for most frequent terms among questions about iPhones

```{r, echo = FALSE}
android_data <- x %>%
  filter(subcategory == "Android Phone")
android_terms <- freq_terms(android_data$text, stopwrds = c("android", "phone"))

iphone_data <- x %>%
  filter(subcategory == "iPhone")
iphone_terms <- freq_terms(iphone_data$text, stopwrds = c("iphone", "phone"))

library(wordcloud)
library(RColorBrewer)

wordcloud(iphone_terms$word, iphone_terms$frequency, scale = c(3, 0.1), max.words = 100, colors = c("grey80", "darkgoldenrod1", "tomato"))
```

##### Word cloud for most frequent terms among questions involving Android Phones

```{r, echo = FALSE}
wordcloud(android_terms$word, android_terms$frequency, scale = c(3, 0.1), max.words = 100, colors = c("grey80", "darkgoldenrod1", "tomato"))
```

@@

survdiff(surv_object~categorized, data = x)
KM_correct <- survfit(surv_object ~ as.factor(categorized), data = x)
plot_surv(KM_correct, data = x, xlim = c(0,100))
```

@@

ggplot(x, aes(x = title_length)) + 
  geom_histogram() + 
  scale_x_continuous("Length of Question Title", breaks = seq(0,100,10)) + 
  ggtitle("Distribution of Title Lengths")
```

* **min title length:** `r min(x$title_length)` characters
* **max title length:** `r max(x$title_length)` characters
* **mean title length:** `r round(mean(x$title_length),2)`
* **median:** `r median(x$title_length)`

@@

```{r, echo = FALSE}
x %>%
  group_by(as.factor(answered)) %>%
  summarise(avg_length = mean(title_length), n = n())

f <- x %>%
  filter(is.na(category))
```

@@

ggplot(x, aes(x = text_length)) + 
  geom_histogram() + 
  scale_x_continuous("Length of Text") + 
  ggtitle("Distribution of Text Lengths")
```

* **min text length:** `r min(x$text_length)` characters
* **max text length:** `r max(x$text_length)` characters
* **mean text length:** `r round(mean(x$text_length),2)` characters
* **median:** `r median(x$text_length)` characters

@@

```{r, echo = FALSE}
x %>%
  group_by(as.factor(answered)) %>%
  summarise(median_length = median(text_length), n = n())
```

@@

```{r, echo = FALSE}
x %>%
  group_by(category) %>%
  summarise(median_length = median(text_length), n = n(), median_time = median(time_until_answer)) %>%
  arrange(desc(median_length))
```

@@

ggplot(x, aes(x = device_length)) + 
  geom_histogram() + 
  scale_x_continuous("Length of Device Name") + 
  ggtitle("Distribution of Device Name Lengths")
```

* **min length:** `r min(x$device_length)` characters
* **max length:** `r max(x$device_length)` characters
* **mean length:** `r round(mean(x$device_length),2)` characters
* **median length:** `r median(x$device_length)` characters

@@

```{r, echo = FALSE}
x %>%
  group_by(as.factor(answered)) %>%
  summarise(avg_length = mean(device_length), n = n())
```

@@

```{r, echo = FALSE}
x %>%
  group_by(category) %>%
  summarise(avg_length = mean(device_length), n = n(), median_time = median(time_until_answer)) %>%
  arrange(median_time)
```

@@

* n_tags included in questions: `r unique(x$n_tags)`
```{r, echo = FALSE}
prop_notags <- sum(x$n_tags == 0)/nrow(x)
```
* `r round(prop_notags*100,2)`% of questions don't have any tags

@@

```{r, echo = FALSE}
sum_stats("n_tags", x)
```

@@

sum_stats("pic_included", x)
```

@@

```{r, echo = FALSE}
survdiff(surv_object ~ as.factor(pic_included), data = x)
KM_pic <- survfit(surv_object~as.factor(pic_included), data = x)
plot_surv(KM_pic, data = x)
plot_surv(KM_pic, data = x, xlim = c(0,250))
```

@@

```{r, echo = FALSE}
sum_stats("new_user", x)
```

##### More summary statistics grouped by new_user

```{r, echo = FALSE}
x %>%
  group_by(new_user) %>%
  summarise(n = n(), include_tag = sum(n_tags != 0)/n, include_pic = sum(n_images != 0)/n, mean_title = mean(title_length), mean_text = mean(text_length), mean_device = mean(device_length))
```

##### wordclouds for new users

* to see if there's a difference in the topics of the questions that new/continuing users ask

```{r, echo = FALSE}
new <- x %>%
  filter(new_user == 1)

new_freq <- freq_terms1(new$text)
wordcloud(new_freq$word, new_freq$frequency, scale = c(3, 0.1), max.words = 100, colors = c("grey80", "darkgoldenrod1", "tomato"))
```

##### wordclouds for continuing users

```{r, echo = FALSE}
continuing <- x %>%
  filter(new_user == 0)
cont_freq <- freq_terms1(continuing$text)
wordcloud(cont_freq$word, cont_freq$frequency, scale = c(3, 0.1), max.words = 100, colors = c("grey80", "darkgoldenrod1", "tomato"))
```

@@

```{r, echo = FALSE}
x$post_datetime <- as.POSIXct(x$post_date,origin="1970-01-01")
x$post_d <- format(x$post_datetime, "%m/%d/%y")
x$post_time <- format(x$post_datetime, " %H:%M:%S")
x$post_weekday <- factor(weekdays(x$post_datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
x$post_hour <- as.numeric(format(x$post_datetime,"%H"))

@@

```{r, echo = FALSE}
sum_stats("post_weekday", x)
```

@@

```{r, echo = FALSE}
sum_stats("post_hour", x)
```

@@

##### log-rank test and survival curves for hour of the day

```{r, echo = FALSE}
survdiff(surv_object ~ as.factor(post_hour), data = x)
KM_hour <- survfit(surv_object ~ as.factor(post_hour), data = x)
plot_surv(KM_hour, data = x)
```
